---
title: "dundunLabels"
author: "Lauren Fink"
contact: lauren.fink@ae.mpg.de 
output: html_document
  toc: True
---


# About

This document steps through all analyses reported in:

Fink, L., Hörster, M., Poeppel, D., Wald-Fuhrmann, M., & Larrouy-Maestri, P. (2023, submitted). Semantic and acoustic features underlying speech-music categories. Pre-print available at: TODO

If using anything from this repository (https://github.com/lkfink/Dundun2_labels), please cite the above paper. 

## Running this code
As long as you have kept the repository structure intact, and you have all required packages installed on your own machine, you should be able to run this code as is, without changing any file paths. The `here` package is used to make all paths relative to the location of this script. Custom functions on which this script relies can be found in the `functions.R` file. Required packages can be found in the `dependencies.R` file. 

# Preparation 
Below we load the packages and data that we will use throughout this script. 
Note that all required packages are listed in the file in this repository called `'dependencies.R'`
If you want to plot figures inline, set op = 0. If you want to output figures to file, set op = 1. Note that when saving figures to file, sometimes the R graphics device can encounter issues and will need to be reset.
```{r, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
here::i_am("dundunLabel_analyses.Rmd")
library(here)
source(here("dependencies.R"))
source(here("functions.R"))
op = 0 # flag if want to save output plots to files (1) or plot inline (0)
```

## Load data
Note that we have two sets of data, collected during experiments in which participants were given the labels "music-like" and "speech-like," or "group 1" and "group 2," respectively. Internally, we referred to these datasets as with labels (wl) and no labels (nl).
```{r}
# Mean acoustic features for for each stimulus
af = read.csv(file = here("data/acousticFeatures.csv"), header=TRUE)

# Exp. 1 dataframe containing participants' music / speech grouping for each stimulus
wl_positions = read.csv(file = here("data/wl_positions.csv"), header=TRUE, sep=",")

# Exp. 2 dataframe containing the position (left or right) where each stimulus placed
nl_positions = read.csv(file = here("data/nl_positions.csv"), header=TRUE, sep=",")

# Exp. 2: labels participants gave to each box after sorting the stimuli
nl_labels = read.csv(file = here("data/nl_labels.csv"), header=TRUE, sep = ",")
```

# Analyses

## Heatmap of raw grouping data
Below, we plot each participants' placement of each stimulus into the speech / music box (Exp. 1) or right / left box (Exp. 2). There is no sorting of rows or columns. Columns are the same in each plot, according to stimulus name. Each row represents an individual participant. 

We also run a t-test to determine if participants display a bias to place more stimuli into music vs. speech (Exp. 1) or on the left side vs the right side (in Exp. 2). Note that while the side music / speech occurred on was counterbalanced in Exp. 1, there was no such counterbalancing equivalent for Exp. 2.
Exp. 1: 1 = speech; 2 = music
Exp. 2: 1 = left; 2 = right
```{r}
# Plot and save to file or print in line
if(op){
  postscript(here("figures/wl_raw.ps"),  width=10, height=nrow(wl_positions)/10)
  plotHeatmap(wl_positions, 1)
  dev.off()
}else {
  plotHeatmap(wl_positions, 1)
}

# Exp. 1
checkSideBias(wl_positions)

# Plot
if(op){
  postscript(here("figures/nl_raw.ps"),  width=10, height=nrow(nl_positions)/10)
  plotHeatmap(nl_positions, 2)
  dev.off()
}else {
  plotHeatmap(nl_positions, 2)
}

# Exp. 2
checkSideBias(nl_positions)

```

## (Dis)similarity in participants' stimulus groupings
Below, we calculate dissimilarity matrices from participants stimulus groupings and plot the results.
Warmer colors = greater similarity; cooler colors = more dissimilar. Note that even though there was a significant difference in how many stimuli participants placed in each box, it does not matter for these subsequent analyses as they are only concerned with which stimuli get grouped with which others (regardless of side).
```{r}
# Calculate number of times each stimlus placed with each other 
wl_groupings = get_groupings(wl_positions)
nl_groupings = get_groupings(nl_positions)

# get distance matrix
wl_dist <- get_dist(wl_groupings, stand = FALSE, method = "euclidean")
nl_dist <- get_dist(nl_groupings, stand = FALSE, method = "euclidean")

# Plot distances
if(op){
  postscript(here("figures/wl_dissim.ps"),  width=10, height=10)
  fviz_dist(wl_dist,
     gradient = list(low = "red", mid = "yellow", high = "blue4"), lab_size = 16, order = FALSE)
  dev.off()
} else {
  fviz_dist(wl_dist,
     gradient = list(low = "red", mid = "yellow", high = "blue4"), lab_size = 16, order = FALSE)
}

if(op){
  postscript(here("figures/nl_dissim.ps"),  width=10, height=10)
  fviz_dist(nl_dist,
     gradient = list(low = "red", mid = "yellow", high = "blue4"), lab_size = 16, order = FALSE)
  dev.off()
} else {
  fviz_dist(nl_dist,
   gradient = list(low = "red", mid = "yellow", high = "blue4"), lab_size = 16, order = FALSE)
}
```

## Dendrograms of stimulus groupings 
From the dissimilarity matrices, we can arrange the stimuli into a dendrogram (again, based on participants' groupings). 
We do this first for Exp. 1, then Exp. 2

### Exp. 1
Calculate dendrogram
```{r}
# Calculate dendogram
wl_hc = get_dendro(wl_groupings)
```

Plot dendrogram
```{r}
# Plot dendrogram

# Define custom color palettes
colorBlind2 <- c("#88CCEE", "#CC6677")

# Plot
wl_dend = fviz_dend(wl_hc, show_labels = TRUE, palette = colorBlind2, as.ggplot = TRUE, cex = 1.5, color_labels_by_k = TRUE, lwd=2, rect=FALSE)
if(op){
  postscript(here("figures/wl_dend.ps"),  width=10, height=10)
  wl_dend
  dev.off()
} else {
  wl_dend
}
```

### Exp. 2
Calculate dendrogram
```{r}
nl_hc = get_dendro(nl_groupings)
```

Plot dendrogram
N.B.: In the dendrogram figure of the final paper, the larger branches were recolored manually in Adobe Illustrator to make the distinctions between branches match with the coloring of the word clouds created below. 
```{r}
# Define color palette
colorBlind10 <- c("#DDCC77", "#117733", "#332288", "#AA4499", 
                             "#44AA99", "#999933", "#882255", "#661100")#, "#6699CC", "#888888")

# Visualize dendrogram
nl_dend = fviz_dend(nl_hc, show_labels = TRUE, palette = colorBlind10, as.ggplot = TRUE, cex = 1.5, color_labels_by_k = TRUE, lwd=2, rect=FALSE)
  

if(op){
  postscript(here("figures/nl_dend.ps"),  width=10, height=10)
  nl_dend
  dev.off()
} else {
  nl_dend
}
```

## PCA of participants' groupings
### Exp. 1
```{r}
# order colors according to cluster. N.B. this is not an optimal way to define colors. Should be able to grab them dynamically, but I cannot figure out where. Have cross-referenced stim labels with colors from previous dendrogram. Can plot labels using: 
# fviz_cluster(wl_hc, repel=TRUE, addEllipses=FALSE, labelsize = 16, show.clust.cent = FALSE, stand=TRUE, shape = 1, main="") 
ccols_ordered = colorBlind2[c(2,1)]

# run pca and initialize plot
wl_pca = fviz_cluster(wl_hc, repel=TRUE, geom="point", pointsize = 12, addEllipses=FALSE, labelsize = 16, show.clust.cent = FALSE, stand=TRUE, shape = 1, main="") 

# define colors based on cluster order and output plot
if(op){
  postscript(here("figures/wl_pca.ps"),  width=10, height=10)
  wl_pca + scale_colour_manual(values = ccols_ordered) + scale_fill_manual(values = ccols_ordered) + theme_classic()
  dev.off()
} else {
  wl_pca + scale_colour_manual(values = ccols_ordered) + scale_fill_manual(values = ccols_ordered) + theme_classic()
}
```

### Exp. 2
```{r}
# define colors based on cluster order. See note above about this not being optimal syntax
ccols_ordered = colorBlind10[c(1,3,6,7,8,2,5,4)] 
# again, I have confirmed that colors match previous dendrogram. I would just use the plot with labels but they overlap too much to fit nicely.
#nl_pca = fviz_cluster(nl_hc, repel=TRUE, addEllipses=FALSE, labelsize = 16, show.clust.cent = FALSE, stand=TRUE, shape = 1) 

# run pca and initialize plot
nl_pca = fviz_cluster(nl_hc, repel=TRUE, geom="point", pointsize = 12, addEllipses=FALSE, labelsize = 16, show.clust.cent = FALSE, stand=TRUE, shape = 1) 

# update colors and output plot
if(op){
  postscript(here("figures/nl_pca.ps"),  width=10, height=10)
  nl_pca + scale_colour_manual(values = ccols_ordered) + scale_fill_manual(values = ccols_ordered) + theme_classic() 
  dev.off()
} else {
  nl_pca + scale_colour_manual(values = ccols_ordered) + scale_fill_manual(values = ccols_ordered) + theme_classic() 
}

```


## Acoustic predictors of PCA dimensions
As can be seen in the correlation matrix below, many of the extracted acoustic features are highly correlated with one another. Therefore, we cannot include all of them in regression models to predict the behavioral data. Additionally, using ~15 features to predict 30 stimulus positions would result in over-fitting. Using PCA solves both of our problems: we reduce dimensionality and remove co-linearity. 

### Correlations among acoustic features
```{r}
a = af[,4:20] # subset data to just include features
chart.Correlation(a)
```

### PCA of acoustic features
```{r}
# fix af stim names for future concatenation with other tables and modeling
af$stim_cat = as.character(af$stim_cat)
af$stim_num = as.character(af$stim_num)
af$stim = paste(af$stim_cat, af$stim_num, sep="")

# do pca on all acoustic features (remove stimulus label cols 1-3)
res.pca_acoust <- prcomp(af[,-(1:3)], scale = TRUE, center = TRUE)

# plot eigen scree
fviz_eig(res.pca_acoust, addlabels = TRUE)

# print eigen values for all PCs
eig.val <- get_eigenvalue(res.pca_acoust)
eig.val
```
In the above plot, we can see a very clear elbow occurs at Dim.5. Also all eigen values after PC4 are less than 1, meaning they explain less variance than an individual variable alone. Therefore, we proceed with PCs 1-4. It is questionable whether we should keep dim. 5 since its eigen value is very near to 1. It is dominated by spectral flux. But given the scree plot, we should not. Just to double check, I have re-run all regression analyses below while keeping dim. 5 and the results do not change (likely because, in the current case, spectral flux is highly correlated with IOI differences, timbre, pitch, etc). 

### Variances explained and the contributions of each feature on each PC
Print summaries
Variable meanings:
var$coord: coordinates of variables to create a scatter plot
var$cos2: represents the quality of representation for variables on the factor map. It’s calculated as the squared coordinates: var.cos2 = var.coord * var.coord.
var$contrib: contains the contributions (in percentage) of the variables to the principal components. The contribution of a variable (var) to a given principal component is (in percentage) : (var.cos2 * 100) / (total cos2 of the component).
```{r}
# number of PCs to keep
pcdims = 4 

# Print eigenvalues
eig.val[c(1:pcdims),]

# change var names to be shorter
row.names(res.pca_acoust$rotation) = c("intensity mean", "intensity diff", "pitch mean", "pitch diff", "timbre mean", "timbre diff", "IOI mean", "IOI diff", "ratio mean", "ratio diff", "pulse clarity", "spectral flux", "recurrence", "mean recur length", "max recur length", "determinism", "AMS peak")
  
# Contributions of each feature to each PC
res.feats <- get_pca_var(res.pca_acoust)
#res.feats$contrib[,c(1:pcdims)] # Contributions to the PCs (in percent)
#res.feats$cos2                   # Quality of representation 
#res.feats$coord                  # Coordinates

# Write to table
contribdf = as.data.frame(res.feats$contrib[,c(1:pcdims)])
round(contribdf, digits=2)


# print out loadings of each var for each PC
# loadings <- res.pca_acoust$rotation
# loadings[,c(1:4)]

# # Results for individual stims
# res.ind <- get_pca_ind(res.pca_acoust)
# res.ind$coord          # Coordinates
# res.ind$contrib        # Contributions to the PCs
# res.ind$cos2           # Quality of representation 
```

Add PC scores to acoustic features data frame 
For easy reference and future modeling
```{r}
# Scores on each PC for each stimulus
pc_scores = res.pca_acoust$x

# TODO automate.. how to assign col names dynamically in R? 
# add scores for PCs 1-4 to our AF data frame
af$PC1 = pc_scores[,1]
af$PC2 = pc_scores[,2]
af$PC3 = pc_scores[,3]
af$PC4 = pc_scores[,4]

# Create new df for easier future modeling
newaf = subset(af[,c(1,21:24)])
```


### Construct lms to predict behavioral sorting pca coord from acoustic PCs
We use a custom function here for running models (see functions.R), then we print our results to a nicely formatted APA style table. CIs are estimated via bootstrapping. Model error (mean absolute error) is estimated using cross-validation. We run a model for both experiments and both dimensions of the behavioral stimulus sorting PCA. Stimulus position in the given dimension is the dependent variable and all four acoustic PCs are the predictors. 

#### Exp. 1
```{r}
modelRes12 = getModelRes(wl_pca, newaf)

# Print results to nice APA table
if(op){
  apa.reg.boot.table(modelRes12[1][[1]], table.number = 2, filename = here("figures/Exp1regX.doc"))
  apa.reg.boot.table(modelRes12[2][[1]], table.number = 3, filename = here("figures/Exp1regY.doc"))
} else {
  print(apa.reg.boot.table(modelRes12[1][[1]], table.number = 2))
  print(apa.reg.boot.table(modelRes12[2][[1]], table.number = 3))
}
```


#### Exp. 2
```{r}
# Experiment 2 
modelRes34 = getModelRes(nl_pca, newaf)

# Print results to nice APA table
if(op){
  apa.reg.boot.table(modelRes34[1][[1]], table.number = 4, filename = here("figures/Exp2regX.doc"))
  apa.reg.boot.table(modelRes34[2][[1]], table.number = 5, filename = here("figures/Exp2regY.doc"))
} else {
  print(apa.reg.boot.table(modelRes34[1][[1]], table.number = 4))
  print(apa.reg.boot.table(modelRes34[2][[1]], table.number = 5))
}

```


##### Create biplot for dims 1+3 then 2+3. 
Based on regression results for Exp. 2
```{r}
# change row names to be our stimulus names
row.names(res.pca_acoust$x) = af$stim

# Create groups
group <- c(rep("Music", times=15), rep("Speech", times=15))

# Initialize plot for first dim of sorting behavior regression results
d13 = fviz_pca_biplot(res.pca_acoust, axes = c(1,3), repel = TRUE, pointsize=1, pointshape=21, col.var="black", label="all", labelsize=4, col.ind=group, palette=colorBlind2, addEllipses=TRUE, ellipse.type="confidence", col.circle = "black", title="", invisible="none")

# output plots
if(op){
  postscript(here("figures/biplot_d13.ps"),  width=10, height=10)
  print(d13 + theme_classic())
  dev.off()
} else{
  d13
}
```

```{r}
# Initialize plot for second dim of sorting behavior regression results
d23 = fviz_pca_biplot(res.pca_acoust, axes = c(2,3), repel = TRUE, pointsize=1, pointshape=21, col.var="black", label="all", labelsize=4, col.ind=group, palette=colorBlind2, addEllipses=TRUE, ellipse.type="confidence", col.circle = "black", title="", invisible="none", max.overlaps = 15)

# output plots
if(op){
  postscript(here("figures/biplot_d23.ps"),  width=10, height=10)
  print(d23 + theme_classic())
  dev.off()} else{
  d23
}
```

## Text Analyses
In this section, we analyze participants labels from Experiment 2, as well as the description of the strategy participants used to categorize the stimuli in both experiments. 

### Frequency of individual words in labels
Create bar chart of frequencies and word clouds
Need to do a little clean up labels first
NOTE: wordclouds display better in file than in line. 
Also note that this analysis is on the word level (ignores full phrases)
```{r}
# get our labels into data frame
labs = nl_labels

# make sure it is char
labs$left_box = as.character(labs$left_box)
labs$right_box = as.character(labs$right_box)

# get into individual words, rather than phrases
# each word stays associated with participant id
labs$id = rownames(labs)
llist <- strsplit(labs$left_box, " ")
ndl = data.frame(Id=rep(labs$id, sapply(llist, length)), Words=unlist(llist))

# do same thing for right box
rlist <- strsplit(labs$right_box, " ")
ndr = data.frame(Id=rep(labs$id, sapply(rlist, length)), Words=unlist(rlist))

# combine right and left into one table again
cleanedlabs = rbind(ndl, ndr)

# clean up words that mean the same thing
cleanedlabs$Words = gsub("afro","african",cleanedlabs$Words)
cleanedlabs$Words = gsub("rythmic","rhythmic",cleanedlabs$Words)
cleanedlabs$Words = gsub("non","no",cleanedlabs$Words)
cleanedlabs$Words = gsub("drums","drum",cleanedlabs$Words)
cleanedlabs$Words = gsub("dunun","dundun",cleanedlabs$Words)
cleanedlabs$Words = gsub("percurssion","percussion",cleanedlabs$Words)
cleanedlabs$Words = gsub("base","bass",cleanedlabs$Words)
cleanedlabs$Words = gsub("load","loud",cleanedlabs$Words)
cleanedlabs$Words = gsub("with","",cleanedlabs$Words)
cleanedlabs$Words = gsub(",","",cleanedlabs$Words)
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="")),] 
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="for")),] 
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="or")),] 
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="the")),] 
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="a")),] 
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="in")),] 
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="through")),]
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="no")),] 
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="1")),] 
cleanedlabs <- cleanedlabs[!apply(cleanedlabs, 1, function(x) any(x=="2")),] 
```


### Make word cloud of raw labels
```{r}
# get organized for word cloud
df = as.matrix(cleanedlabs$Words)
df = tolower(df) # make sure all lowercase
tabled = table(df)

# plot label frequencies
barplot(sort(tabled, decreasing = FALSE), las=2, cex.names=.7, horiz=TRUE, xlim = c(0,25))

# make word cloud
set.seed(1234) # for reproducibility
dframe = data.frame(tabled) # convert back to data table

# create word cloud
if(op){
  postscript(here("figures/general_wordCloud.ps"),  width=10, height=10)
  wordcloud(words = dframe$df, freq=dframe$Freq, min.freq = 1, 
          max.words=200, random.order=FALSE, rot.per=0, 
          scale=c(4,.5))
  dev.off()
} else {
  wordcloud(words = dframe$df, freq=dframe$Freq, min.freq = 1, 
          max.words=200, random.order=FALSE, rot.per=0, 
          scale=c(4,.5))
}
```

### Analyze labels by cluster
First, we need to make a new table with labels for each stimulus
```{r}
# Create new data frame with labels mapped onto stimuli
stimlabs = nl_positions
for (irow in 1:nrow(stimlabs)){
  for (icol in 1:30){
    currside = stimlabs[irow,icol]
    if (currside == 1) #1 is left 
      stimlabs[irow, icol] = labs$left_box[irow]
    else {
      stimlabs[irow, icol] = labs$right_box[irow]
    }
    
    # do some of the same cleaning as we did before
    # we don't need to do as much now because the words are still in their phrase, rather than individual
    stimlabs[irow, icol] = gsub(",","",stimlabs[irow, icol])  
    stimlabs[irow, icol] = gsub("afro","african",stimlabs[irow, icol])
    stimlabs[irow, icol] = gsub("drums","drum",stimlabs[irow, icol])
    stimlabs[irow, icol] = gsub("dunun","dundun",stimlabs[irow, icol])
    stimlabs[irow, icol] = gsub("percurssion","percussion",stimlabs[irow, icol])
    stimlabs[irow, icol] = gsub("base","bass",stimlabs[irow, icol])
    stimlabs[irow, icol] = gsub("rythmic","rhythmic",stimlabs[irow, icol])
    stimlabs[irow, icol] = gsub("melodies","melodic",stimlabs[irow, icol])
    stimlabs[irow, icol] = gsub("load","loud",stimlabs[irow, icol])
  } 
}
```

Now we make lists of labels corresponding to each cluster
```{r}
# get stim / cluster number mapping
stimclusters = nl_hc$cluster
f = data.frame(lapply(stimclusters, type.convert), stringsAsFactors=FALSE)

# loop through clusters and save stimulus labels
nclusts = max(f)
clustlabels = list()
for (iclust in 1:nclusts){
  indices = which(f %in% iclust) # get stim cols corresponding to this cluster
  # make vector of labels from these cols
  tmp = stimlabs[,indices]
  if (length(indices) > 1){ # more than one stim for this cluster
    clustlabels[[iclust]] = paste(tmp, sep = ',') #combine string vectors for each stim 
    }
  else {clustlabels[[iclust]] = tmp}
}
```

Create document term matrix with the labels for each cluster
```{r}
# create corpus of docs
docs <- Corpus(VectorSource(stimlabs)) %>% 
  #tm_map(removePunctuation) %>% # this is introducing extra c character.. 
  tm_map(stripWhitespace) %>%
  tm_map(content_transformer(tolower)) %>%
  tm_map(content_transformer(removePunctuation)) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(removeWords, stopwords("SMART")) #%>%
  #tm_map(stemDocument, language="english") 

# convert to term document matrix
tdm <- TermDocumentMatrix(docs) 
```

### Report some descriptive stats
Associations = terms that correlate in the matrix 
```{r}
#findFreqTerms(tdm, 60)
findAssocs(tdm, "high", 0.8)
findAssocs(tdm, "low", 0.8)

findAssocs(tdm, "fast", 0.8)
findAssocs(tdm, "slow", 0.8)

findAssocs(tdm, "rhythmic", 0.8)
findAssocs(tdm, "arhythmic", 0.8)

```

### Prepare for comparison clouds (difference between clouds)
We want to do this on multiple levels
NB. cluster number in dendrogram is weird (not from left to right)
- plotting all clusters 1:8 = lowest level
- 1,6 vs. 2; 8:7 vs. 3:5 = medium
- 1,2,6 vs. 8,7,3,4,5 = highest level
```{r}
# convert tdm to data frame for easier handling
tdm = as.matrix(tdm)
dfdtm = data.frame(tdm)
colnames(dfdtm) = colnames(stimlabs)
ndfdtm = dfdtm # make a copy so don't mess up row sums when adding new cols

# high cluster
h1inds = f %in% c(1,2,6)
h2inds = f %in% c(8,7,3,4,5)
ndfdtm$h1 = rowSums(dfdtm[,h1inds]) 
ndfdtm$h2 = rowSums(dfdtm[,h2inds])

# med cluster
m11inds = f %in% c(1,6)
m12inds = f == 2
m21inds = f %in% c(8,7)
m22inds = f %in% c(3:5)

ndfdtm$m11 = rowSums(dfdtm[,m11inds]) 
ndfdtm$m12 = rowSums(dfdtm[,m12inds]) 
ndfdtm$m21 = rowSums(dfdtm[,m21inds]) 
ndfdtm$m22 = rowSums(dfdtm[,m22inds])


# low cluster 
l1inds = f == 1
l2inds = f == 2
l3inds = f == 3
l7inds = f == 7

# NOTE - cannot take rowsums of clusters that only have one stim. basically we just need to repeat that column (for 6,8,4,5)

ndfdtm$l1 = rowSums(dfdtm[,l1inds]) 
ndfdtm$l2 = rowSums(dfdtm[,l2inds]) 
ndfdtm$l3 = rowSums(dfdtm[,l3inds]) 
ndfdtm$l4 = dfdtm$S12
ndfdtm$l5 = dfdtm$S13
ndfdtm$l6 = dfdtm$M4
ndfdtm$l7 = rowSums(dfdtm[,l7inds]) 
ndfdtm$l8 = dfdtm$M13

# normalize by total number of words used in each cluster
ndfdtm_norm = apply(ndfdtm, 2, function(c) c / nrow(ndfdtm)) 
apply(ndfdtm_norm, 2, max) 

# or normalize by using log
ndfdtm_norm_log = ndfdtm
for (icol in ncol(ndfdtm_norm_log)){
   for (irow in nrow(ndfdtm_norm_log)){
     if (ndfdtm_norm_log[irow, icol] != 0){
        ndfdtm_norm_log[irow, icol] = 1 + log(ndfdtm_norm_log[irow, icol])  
     }
   }
}
apply(ndfdtm_norm_log, 2, max) 

# define cluster colors we will use for future plotting
ccols = brewer.pal(n = 8, name = "Dark2")
ccols_ordered = ccols[c(1,3,6,7,8,2,5,4)] # omg such a dumb way to do this.. 
```

### Create comparison clouds
First for highest level cluster
```{r}
forcloud = as.matrix(ndfdtm_norm[,c("h1", "h2")])

if(op){
  postscript(here("figures/nl_compcloud_main.ps"),  width=10, height=10)
  comparison.cloud(forcloud, random.order=FALSE, rot.per=0,
                   title.size=2, max.words=100, colors=c("saddlebrown", "gray"), match.colors=TRUE, title.bg.colors = c("saddlebrown", "gray"))
  dev.off()
} else {
  comparison.cloud(forcloud, random.order=FALSE, rot.per=0,
                   title.size=2, max.words=100, colors=c("saddlebrown", "gray"), match.colors=TRUE, title.bg.colors = c("saddlebrown", "gray"))
}
```

Now for medium level clusters
```{r}
forcloud = as.matrix(ndfdtm_norm[,c("m11", "m12")])

if(op){
  postscript(here("figures/nl_compcloud.ps"),  width=10, height=10)
  comparison.cloud(forcloud, random.order=FALSE, rot.per=0,
                   title.size=2, max.words=100, colors=c("#999933", "#44AA99"), match.colors=TRUE, title.bg.colors = c("#999933", "#44AA99"))
  dev.off()
} else {
  comparison.cloud(forcloud, random.order=FALSE, rot.per=0,
                 title.size=2, max.words=100, colors=c("#999933", "#44AA99"), match.colors=TRUE, title.bg.colors = c("#999933", "#44AA99"))
}

```

```{r}
forcloud = as.matrix(ndfdtm_norm[,c("m21", "m22")])

if(op){
  postscript(here("figures/nl_compcloud2.ps"),  width=10, height=10)
  comparison.cloud(forcloud, random.order=FALSE, rot.per=0,
                   title.size=2, max.words=100, colors=c("#332288", "#DDCC77"), match.colors=TRUE, title.bg.colors = c("#332288", "#DDCC77"))
  dev.off()
} else {
  comparison.cloud(forcloud, random.order=FALSE, rot.per=0,
                   title.size=2, max.words=100, colors=c("#332288", "#DDCC77"), match.colors=TRUE, title.bg.colors = c("#332288", "#DDCC77"))
}
```